Can Auxiliary Indicators Improve COVID-19 Forecasts and Hotspot Prediction?

### 2021-06-13 forecast/paper/paper.tex
Update discussion of case revisions

Vintage training data means different things, in practice, for different
signals. The three signals based on medical claims, CHNG-CLI, CHNG-COVID, and
DV-CLI, are most often 3-5 days latent, and subject to a considerable but
regular degree of revision or ``backfill'' after their initial publication date.
The survey-based signal, CTIS-CLI-in-community, is 2 days latent, and rarely
undergoes any revision at all.  The target variable itself, reported COVID-19
case rates, is 1 day latent, and exhibits frequent, unpredictable revisions
(sometimes clear anomalies) after initial publication.  Compared to the revision
pattern in the medical claims signals, which are appears to be much more
systematic in nature, the revision pattern in the case rates signal can be
highly erratic. Big spikes or other anomalies can occur in the data as reporting
backlogs are cleared, changes in case definitions are made, etc. Groups like JHU 
CSSE then work tirelessly to correct such anomalies (e.g., back-distribute a
huge spike when a reporting backlog is cleared), resulting in highly nontrivial
and unpredictable revisions.

TODO Discuss Google-AA.  We're using all finalized data, but explain why we're
OK with this ... (they never backfill).

@@

>>>>

Vintage training data means different things, in practice, for different
signals. The three signals based on medical claims, CHNG-CLI, CHNG-COVID, and
DV-CLI, are most often 3-5 days latent, and subject to a considerable but
regular degree of revision or ``backfill'' after their initial publication date.
The survey-based signal, CTIS-CLI-in-community, is 2 days latent, and rarely
undergoes any revision at all.  The target variable itself, reported COVID-19
case rates, is 1 day latent, and exhibits frequent, unpredictable revisions
(sometimes clear anomalies) after initial publication.  Compared to the revision
pattern in the medical claims signals, which are much more systematic in nature,
revisions in case reports can be highly erratic. Big spikes or other anomalies
can occur in the data as reporting backlogs are cleared, changes in case
definitions are made, etc. Groups like JHU CSSE then work tirelessly to correct
such anomalies after first publication (e.g., they will attempt to
back-distribute a spike when a reporting backlog is cleared, by working with a
local authority to figure out how this should best be done), which can result
in very nontrivial and often unpredictable revisions.

@@

Lastly, our treatment of the Google-AA signal is different from the rest.
Because Google's team did not start publishing this signal until early
September, 2020, we do not have true vintage data before then.  However, this
signal is never revised after initial publication (confirmed via personal
communication with the Google team that produces this signal), so we simply use
finalized values for it in our analysis.
